%-----------------------------------------
% Sérgio Serrano - serrano.miser [at] gmail.com
% Curriculum Vitae
%
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

\documentclass[11pt,a4paper,final]{moderncv}
\usepackage{fontspec}
\moderncvtheme[darkred]{classic}
\renewcommand{\familydefault}{\sfdefault}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% Personal Information
\firstname{Sérgio}
\familyname{Serrano}
\homepage{about.me/sergioserrano}
\nopagenumbers{}

%-----------------------------------------
%   Begin BODY
%-----------------------------------------

\begin{document}
\maketitle

\section{Education}

\cventry{August 2009 - December 2010}{Master of Science in Information Technology - Information Security}{Carnegie Mellon University}{Pittsburgh, PA}{Final QPA: 3.83}{Thesis: "Security Analysis of Network Neighbors". Advisor: Nicolas Christin.}

% If I want to give more academic detail
%\cventry{Relevant courses:}{}{}{}{} {
%\vspace*{-8.2mm}
%\begin{itemize}\setlength\itemindent{0pt}\begin{itemize}\setlength\itemindent{0pt}
%   \item Secure Software Systems
%    \item Embedded Systems
%    \item Fault-Tolerant Distributed Systems
%    \item Network Security
%    \item Applied Security
% \end{itemize}
%}

\cventry{September 1994 - October 1999}{Bachelor in Electrotechnical Engineering (5 years degree)}{Faculdade de Ciências e Tecnologia, Universidade Nova de Lisboa}{Monte de Caparica, Portugal}{Grade: 14 (0-20 scale)}{}

\section{Experience}

\cventry{February 2021 - Present}{Security Manager}{SaltPay}{}{}{
    \begin{itemize}
        \item Responsible for defining and delivering the information security roadmap;
        \item Responsible for the information security awareness and training programs;
        \item Responsible for compliance initiatives toward security certifications and regulations;
        \item Developer and architect of security solutions;
        \item Provide security guidance to the technology teams during the development lifecycle;
        \item Security auditor of applications and infrastructure;
        \item Tools and Technologies: AWS, Terraform, Vault, Burp, OWASP ZAP, Go, Python, Java.
    \end{itemize}
}

\cventry{April 2016 - January 2021}{Principal Security Engineer}{Talkdesk}{}{}{
    \begin{itemize}
        \item Developer and architect of security solutions;
        \item Responsible for defining the engineering security program;
        \item Security auditor of applications and infrastructure;
        \item Provide security guidance to the engineering teams during the development lifecycle;
        \item Security training for the engineering teams;
        \item Support compliance efforts toward security certifications and regulations;
        \item Tools and Technologies: AWS, Terraform, Packer, Vault, CFSSL, osquery, OSSEC, Burp, OWASP ZAP, ELK stack, BDD, Java, Python.
    \end{itemize}
}

\cventry{November 2015 - March 2016}{Applications Security Team}{Portugal Telecom}{}{}{
    \begin{itemize}
        \item Security auditor of applications and infrastructure;
        \item Developer and advisor for security solutions;
        \item Tools and Technologies: Apache, Apache Tomcat, Nginx, Java, Python, Burp, Git.
    \end{itemize}
}

\cventry{October 2012 - October 2015}{Software Engineer, Security and ID Team}{Portugal Telecom}{}{}{
    \begin{itemize}
        \item Main developer and operations manager of SSO solution (https://login.sapo.pt/, https://wallet.pt);
        \item Main developer and operations manager of the authentication module for a Payments solution (https://wallet.pt);
        \item Main developer and operation manager of identity management solution (https://id.sapo.pt/);
        \item Security solutions development;
        \item CTF organizer and developer for SAPO Codebits;
        \item Tools and Technologies: Apache, Apache Tomcat, Nginx, Java, Spring Framework, Python, Django, Shibboleth, Memcached, SAML, OAuth, OpenID, YubiKey, Git.
    \end{itemize}
}

\cventry{February 2011 – November 2012}{Networking and IT Security Engineer}{Portugal Telecom}{}{}{
    \begin{itemize}
        \item Development of network and IT security architectures;
        \item Development of network security program for SAPO (http://www.sapo.pt/) and residential ISP;
        \item Network security incident handler;
        \item Development of security vulnerabilities management tool based in the Django web framework;
        \item Development of tools to support network operation, maintenance tasks and management reporting;
        \item Tools and Technologies: IP, BGP, Cisco, DPI, OSSIM, Snort, OSSEC, CVSS, Honeypots, ExaBGP, Python, Django, MySQL, Subversion.
    \end{itemize}
}

\cventry{April 2005 – January 2011}{Network Engineer}{Portugal Telecom}{}{}{
    \begin{itemize}
        \item Network engineering for all related services of SAPO (http://www.sapo.pt/);
        \item ISP services network infrastructure development. Includes RADIUS (AAA) and DNS;
        \item ISP core network QoS monitoring and engineering;
        \item Development of tools to support network operation, maintenance tasks and management reporting;
        \item Tools and Technologies: IP, RADIUS (AAA), DNS, Cisco, Alteon, Apache, *NIX, Perl, Cacti, Nagios, Centreon, virtualization.
    \end{itemize}
}

\cventry{April 2001 to March 2005}{Software Developer and Chief Engineer}{Siemens}{}{}{
    \begin{itemize}
        \item xDSL, ATM large scale network provisioning application development for Service Provisioning;
        \item Web reporting applications development for Performance Management;
        \item Tools and Technologies: C++, CORBA, Versant Database, IBM Clearcase control versioning, Apache Tomcat, JSP and Servlets, XML, Adobe Flash and Adobe Coldfusion.
    \end{itemize}
}

\cventry{September 1999 to March 2001}{Pre-Sales Networking Projects Manager}{Telepac}{}{}{
    \begin{itemize}
        \item ISP pre-sales networking projects management and development;
        \item Enterprise technical support for Internet solutions;
        \item Tools and Technologies: xDSL, Frame-Relay, HDLC, IP, Routing, Linux, DNS, SMTP, IMAP, POP3.
    \end{itemize}
}

\section{Technical skills}

\cvline{Languages}{Advanced knowledge of Java, Python and good knowledge of C++, Perl, Bash, Assembly, HTML, XML, JSP, CFML.}
\cvline{Information Security}{Software and network security, cryptography, VPN, DPI, IDS, WAF, FW and honeypots.}
\cvline{Databases}{Relational and Object Oriented Databases.}
\cvline{DevOps}{CI/CD, automation and monitoring systems.}
\cvline{Tools}{Terraform, Packer, Vault, CFSSL, OSSEC, Burp, ELK stack, Eclipse, Vim, Git, Subversion, ClearCase, OTRS, Cacti, Nagios, Centreon.}
\cvline{Networking}{TCP/IP, BGP, Load Balancing. Hands-on experience with Cisco, Nortel and Crossbeam Equipments.}

\section{Languages}

\cvlanguage{Portuguese}{Fluent}{Native language.}
\cvlanguage{English}{Fluent}{Speaking, reading, and writing.}
\cvlanguage{French}{Intermediate}{Speaking, reading, and writing.}
\cvlanguage{Spanish}{Intermediate}{Speaking, reading.}

\section{Interests}

\cvline{Handball}{It's never too late to learn new skills.}
\cvline{Karaté Shotokan}{Keeping the balance since 1986.}
\cvline{BTT}{Riding a bicycle while being surrounded by nature. That is it.}
\cvline{Comics}{Besides being an avid consumer I have also entered the amazing realm of creation with a character named Almiscaro.}
\cvline{Theater}{Before stepping into the world of IT I have worked as a professional actor.}

\end{document}
